\textbf{Advection versus diffusion in intraventricular transport}

### 2025-03-26 paper/main.tex
place figures nicely

\begin{figure}%[H]
    \centering
    \includegraphics[width=\textwidth]{graphics/figure3_compare_experiments_and_simulations.png}
    \caption{
    \textbf{a.} Relative change in fluorescence intensity $\Delta F(t)$ 
    in each region of interest (ROI)
    observed during experiments of photoconversion of Dendra2 proteins in ROI 1. 
    Bold lines are mean values of the cohort and shaded regions cover one standard devation errors
    in the mean.
    \textbf{b.} Mean concentration $\cbar(t)$ in each ROI in a
    simulation of Dendra2 protein transport with
    the diffusion coefficient $D_3$.
    \textbf{c.} Time to $\Delta F(t)$ reaches a threshold value of 0.25 in
    one representative zebrafish larva.
    Time to $\cbar(t)$ reaches a threshold value of 0.25 for
    a transport simulation with diffusion coefficient $D_3$.
    We have excluded the posterior-most regions of the geometries,
    because the values of $\Delta F$ and $\cbar$ never exceeded the threshold
    value of 0.25 in these regions. Scale bars 50 \textmu m.}
    \label{fig:fig3}
\end{figure}
% Final Delta F values
%0.6322650156762044 ROI 2
%0.7059449124175479 ROI 3
%0.6694500367160006 ROI 4
%0.28986700094045437 ROI 5
%0.18155055624229066 ROI 6
% Final mean c values ROIs 2-6: 0.80, 0.76, 0.86, 0.60 and 0.38

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{graphics/figure4_compare_control_mutant.png}
    \caption{\textbf{a.} Relative change in fluorescence intensity $F(t)$
    in each region of interest (ROI) for control (black lines, $n=8$)
    and \emph{smh} mutant (red lines, $n=6$) fish. 
    Bold lines are mean values of the cohorts and shaded regions cover one standard devation errors
    in the means.
    \textbf{b.} Times when $\Delta F(t)$ first exceeds a threshold value,
    equal to 0.25 (ROIs 2--4) or 0.10 (ROIs 5, 6), for control (gray dots) and
    \emph{smh} mutant (red dots) fish.
    The thick black lines denote mean values of the datasets. The $p$-values
    were calculated using a Mann-Whitney U test with a confidence level of 95\%, with 
    the null hypothesis that the two distributions of control and mutant data are 
    from the same population.
    \textbf{c.} Mean concentration $\cbar(t)$ in each ROI,
    simulated using the baseline model (black lines) and the cardiac-only/no-cilia model (red lines).
    The horizontal gray lines mark the threshold value $\hat{c}$, and the time
    $\hat{t}$ when the threshold is first exceeded is reported in the plot legends.
    Note that in both panels \textbf{a} and \textbf{c}, the vertical axes have
    different limits in each plot.}
    \label{fig:fig4}
\end{figure}

@@

The CSF velocities are most strongly
affected when removing cilia in the dorsal part of the middle ventricle,
as the maximum velocity magnitude drops from 27.9 \textmu m/s to 7.9 \textmu m/s.
In vivo, these dorsal cilia generate the strongest flow at
this developmental stage of the fish~(\Crefpanels{fig:fig1}{c})~\cite{Olstad2019CiliaryDevelopment}.
In contrast, removing cilia in the anterior ventricle or the ventral region of the middle
ventricle has minimal impact, and results in maximum speeds
of 27.9 \textmu m/s and 27.4 \textmu m/s, respectively.
Of the total tangential forces exerted by the cilia, ventral cilia in the middle ventricle
contribute with 34\%, while the dorsal cilia exert 52\% of the total tangential
force~(\Crefpanels{fig:fig5}{b}). The magnitude of these force contributions are thus
more similar than the difference in their impact on the maximum velocity magnitudes.

Changes in the transport of Dendra2 are most prominent when removing the dorsal cilia
in the middle ventricle. All mean concentration profiles 
(except ROI 1, where we impose the photoconversion curve)
exhibit changes (\Crefpanels{fig:fig5}{c}).
Compared to the baseline model results, we observe less solute distribution
in the middle and anterior ventricles (ROIs 2--5),
and more rapid transport to the posterior ventricle (ROI 6).
On the other hand, removal of anterior cilia does not alter the 
mean concentrations (\Crefpanels{fig:fig5}{c}).
Finally, without ventral cilia in the middle ventricle,
more solute spreads towards the anterior ventricle (ROI 5) and
less solute spreads towards the posterior ventricle (ROI 6).
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{graphics/figure5_compare_cilia_modifications.png}
    \caption{\textbf{a.} The three separate ciliated regions cilia paralysis is simulated
    by imposing a zero tangential traction boundary condition in the respective region.
    \textbf{b.} The total tangential force applied with the tangential traction
    boundary condition in the three separate ciliated regions, as well as the total
    (the sum of the three regions), calculated with \Cref{eq:tangential_force_calculation}. 
    \textbf{c.} Mean concentration $\cbar(t)$ for the six regions of interest (ROIs) in the three 
    paralysis scenarios considered. The region named in the legend is the region
    where we modify the cilia tangential traction boundary condition to a free-slip condition
    in the CSF flow model.}
    \label{fig:fig5}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.975\textwidth]{graphics/figure3_compare_experiments_and_simulations.png}
    \caption{
    \textbf{a.} Relative change in fluorescence intensity $\Delta F(t)$ 
    in each region of interest (ROI)
    observed during experiments monitoring
    the movement of Dendra2 proteins photoconverted by laser targeting ROI 1. 
    Bold lines are mean values of the cohort ($n=8$) and shaded regions cover
    one standard devation errors in the mean.
    \textbf{b.} Mean concentration $\cbar(t)$ in each ROI in a
    simulation of Dendra2 protein transport with
    the diffusion coefficient $D_3$.
    \textbf{c.} Time to $\Delta F(t)$ reaches a threshold value of 0.25 in
    one representative zebrafish larva.
    \textbf{d.} Time to $\cbar(t)$ reaches a threshold value of 0.25 for
    a transport simulation with diffusion coefficient $D_3$.
    We have excluded the posterior-most regions of the geometries,
    because the values of $\Delta F$ and $\cbar$ never exceeded the threshold
    value of 0.25 in these regions. Scale bars 50 \textmu m.}
    \label{fig:fig3}
\end{figure}
% Final Delta F values
%0.6322650156762044 ROI 2
%0.7059449124175479 ROI 3
%0.6694500367160006 ROI 4
%0.28986700094045437 ROI 5
%0.18155055624229066 ROI 6
% Final mean c values ROIs 2-6: 0.80, 0.76, 0.86, 0.60 and 0.38

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{graphics/figure4_compare_control_mutant.png}
    \caption{\textbf{a.} Relative change in fluorescence intensity $\Delta F(t)$
    in each region of interest (ROI) for control (black lines, $n=8$)
    and \emph{smh} mutant (red lines, $n=6$) fish. 
    Bold lines are mean values of the cohorts and shaded regions cover one standard devation errors
    in the means.
    \textbf{b.} Times when $\Delta F(t)$ first exceeds a threshold value,
    equal to 0.25 (ROIs 2--4) or 0.10 (ROIs 5, 6), for control (gray dots) and
    \emph{smh} mutant (red dots) fish.
    The thick black lines denote mean values of the datasets. The $p$-values
    were calculated using a Mann-Whitney U test with a confidence level of 95\%, with 
    the null hypothesis that the two distributions of control and mutant data are 
    from the same population.
    \textbf{c.} Mean concentration $\cbar(t)$ in each ROI,
    simulated using the baseline model (black lines) and the cardiac-induced/no-cilia model (red lines).
    The horizontal gray lines mark the threshold value $\hat{c}$, and the time
    $\hat{t}$ when the threshold is first exceeded is reported in the plot legends.
    Note that in both panels \textbf{a} and \textbf{c}, the vertical axes have
    different limits in each plot.}
    \label{fig:fig4}
\end{figure}

@@

The CSF velocities are most strongly
affected when removing cilia in the dorsal part of the middle ventricle,
as the maximum velocity magnitude drops from 27.9 \textmu m/s to 7.9 \textmu m/s.
In vivo, these dorsal cilia generate the strongest flow at
this developmental stage of the fish~(\Crefpanels{fig:fig1}{c})~\cite{Olstad2019CiliaryDevelopment}.
In contrast, removing cilia in the anterior ventricle or the ventral region of the middle
ventricle has minimal impact, and results in maximum speeds
of 27.9 \textmu m/s and 27.4 \textmu m/s, respectively.
Of the total tangential forces exerted by the cilia, ventral cilia in the middle ventricle
contribute with 34\%, while the dorsal cilia exert 52\% of the total tangential
force~(\Crefpanels{fig:fig5}{b}). The magnitude of these force contributions are thus
more similar than the difference in their impact on the maximum velocity magnitudes.
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{graphics/figure5_compare_cilia_modifications.png}
    \caption{\textbf{a.} The three separate cilia regions for which cilia paralysis is simulated
    by imposing a zero tangential traction boundary condition in the respective region.
    \textbf{b.} The total tangential force applied to the boundary with the tangential traction
    boundary condition in each of the three separate ciliated regions, as well as the total force
    (the sum of the three regions), calculated with \Cref{eq:tangential_force_calculation}. 
    \textbf{c.} Mean concentration $\cbar(t)$ for the six regions of interest (ROIs) in the three 
    paralysis scenarios considered. The region named in the legend is the region
    where we modify the cilia tangential traction boundary condition to a free-slip condition
    in the CSF flow model.}
    \label{fig:fig5}
\end{figure}

Changes in the transport of Dendra2 are most prominent when removing the dorsal cilia
in the middle ventricle. All mean concentration profiles 
(except ROI 1, where we impose the photoconversion curve)
exhibit changes (\Crefpanels{fig:fig5}{c}).
Compared to the baseline model results, we observe less solute distribution
in the middle and anterior ventricles (ROIs 2--5),
and more rapid transport to the posterior ventricle (ROI 6).
On the other hand, removal of anterior cilia does not alter the 
mean concentrations (\Crefpanels{fig:fig5}{c}).
Finally, without ventral cilia in the middle ventricle,
more solute spreads towards the anterior ventricle (ROI 5) and
less solute spreads towards the posterior ventricle (ROI 6).
